\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-23 paper.qmd
Update the Figure title

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best number of bins, low density bin and large edge removal. Both (a) and (c) show MSE, against number of bins and standardised count. A good benchmark value for these parameters is when the MSE drops and then flattens out."
# Distribution of $2\\text{-}D$ Euclidean distances between bin centroids of the triangular mesh generated with S-curve UMAP data.
#| label: fig-dist-scurve
#| out-width: 100%
#| fig-width: 8
#| fig-height: 6
#| fig-pos: H

>>>>

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best number of bins, low density bin and large edge removal. Both (a) and (c) show MSE, against number of bins and standardised count. A good benchmark value for these parameters is when the MSE drops and then flattens out. Plot (b) shows the distribution of stadardised counts of hexagons. Plot (c) shows the distribution of $2\\text{-}D$ Euclidean distances between bin centroids, with a good benchmark value for removing large edges would being the distance that shows the first large increase."

#| label: fig-dist-scurve
#| out-width: 100%
#| fig-width: 8
#| fig-height: 6
#| fig-pos: H

### 2024-06-23 paper.tex
Update the Figure title

\caption{\label{fig-bins-scurve}Hexbin plots from different number of
bins for the UMAP applied to S-curve data: (a) \(b = 91\) (7, 13), (b)
\(b = 190\) (10, 19), and (c) \(b = 364\) (14, 26). The hexbins are
colored based on the density of points, with darker colors indicating
higher density and yellow color representing lower density within each
bin. What is the number of bins that would be effective?}

@@

\caption{Various plots to help assess best number of bins, low density
bin and large edge removal. Both (a) and (c) show MSE, against number of
bins and standardised count. A good benchmark value for these parameters
is when the MSE drops and then flattens out.}

>>>>

\caption{\label{fig-bins-scurve}Hexbin plots from different number of
bins for the UMAP applied to S-curve data: (a) \(b = 91\) (7, 13), (b)
\(b = 264\) (12, 22), and (c) \(b = 364\) (14, 26). The hexbins are
colored based on the density of points, with darker colors indicating
higher density and yellow color representing lower density within each
bin. What is the number of bins that would be effective?}

@@

\caption{Various plots to help assess best number of bins, low density
bin and large edge removal. Both (a) and (c) show MSE, against number of
bins and standardised count. A good benchmark value for these parameters
is when the MSE drops and then flattens out. Plot (b) shows the
distribution of stadardised counts of hexagons. Plot (c) shows the
distribution of \(2\text{-}D\) Euclidean distances between bin
centroids, with a good benchmark value for removing large edges would
being the distance that shows the first large increase.}
